---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# landmark

```{r, echo=FALSE, message=FALSE, results=FALSE}
devtools::load_all()
```

Calculate landmark sets for finite metric spaces using the maxmin procedure (for fixed-radius balls) or an adaptation of it for rank data (for roughly fixed-cardinality nearest neighborhoods).

```{r example}
(x <- matrix(c(1, 2, 4, 4), dimnames = list(letters[1:4], "x")))
```

## `maxmin` procedure

The original `maxmin` procedure produces a landmark set for covering a point cloud with either of two minimal ball covers:

* a minimum number of balls of fixed common radius
* a fixed number of balls of minimum common radius

```{r maxmin example}
landmarks_maxmin(x, eps = 3.5)
landmarks_maxmin(x, eps = 1.5)
landmarks_maxmin(x, eps = 0.5)
```

## "`lastfirst`" procedure

An adaptation of `maxmin` to ranked distances will produce a landmark set for covering a point cloud with either of two minimal neighborhood covers:

* a minimum number of neighborhoods of roughly fixed common cardinality
* a fixed number of neighborhoods of minimal roughly common cardinality

```{r lastfirst example}
landmarks_lastfirst_cory(x, cardinality = 4)
landmarks_lastfirst_cory(x, cardinality = 3)
landmarks_lastfirst_cory(x, cardinality = 2)
landmarks_lastfirst_cory(x, cardinality = 1)
```

# workflow

Foundations have been adapted from `peekxc/Mapper`.

We should each edit only our respective functions `landmarks_lastfirst_*()` as we attempt to implement the algorithm discussed on 2020-05-21, in the branches `lastfirst/*` (`cory` and `yara`: experimental; `main`: consolidated).

If changes are made to other files then they should be committed to a new branch first.

# reference

Rigorous definitions, algorithms, examples, and exposition are underway at [this Overleaf project](https://www.overleaf.com/read/fpjrtgfjstyx).
